---
title: "Lab 7 Assignment: Group 02"
format:
  html:
    embed-resources: true
editor: visual
---

## Micro-report lab 07

Our group:

| Name                        | Student ID |
|-----------------------------|------------|
| Lukas Kjær Sebblow          | s225071    |
| Hans Christian M. Henriksen | s224987    |
| Mia Thao Enné               | s225029    |
| Fabrice Tangih Fongwa       | s240038    |

### Loading the data

The data is taken from “PCA tidyverse style” by Claus O. Wilke, Professor of Integrative Biology. It's a biopsy data set, based on breast cancer patients from the University of Wisconsin Hospital. The doctor in charge assessed biopsies from 699 patients.

We're loading the data, and since it's a dataset on biopsies, that's what we will call it.

```{r}
#| echo: False
library(tidyverse)
biopsy <- read_csv('https://wilkelab.org/classes/SDS348/data_sets/biopsy.csv')
biopsy
```

### The distribution of benign and malignant outcomes 

```{r}
p1 <- biopsy |> 
  count(uniform_cell_size, 
        outcome) |> 
  ggplot(aes(uniform_cell_size, 
             n, 
             fill = outcome)) + 
  geom_col(position = position_dodge(preserve = "single"),
           color = "black",
           alpha = 0.5) +
  geom_hline(yintercept = 0) +
  theme_minimal() +
  theme(legend.position = "bottom") +
  labs(x = "Uniform cell size",
      y = "Count",
      title = "The distribution of uniform cell size")

p2 <- biopsy |> 
  ggplot(aes(clump_thickness,
             outcome,
             fill = outcome)) +
  geom_boxplot(alpha = 0.5) + 
  theme_minimal() +
  theme(legend.position = "bottom") +
  labs(x = "Clump thickness",
       y = "Outcome",
       titel = "The distribution of clump thickness")
```

Fist we look at the dispersion when looking at uniform cell size biopsies:

```{r}
p1
```

Now we look at the clump thickness:

```{r}
p2
```
